---
title: "example"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{example}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
Suggests: knitr, rmarkdown
VignetteBuilder: knitr
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
# Setup:
```{r setup}
library(GRADA)
library(parallel)
library(DT)
library(rmarkdown)
```
## Example Data:
```{r load example data}
# The example data from Phage - SRX6454172 (first 100 reads) can be used to test the function.
read1 <- system.file("extdata", "grada_R1.fastq", package = "GRADA")
read2 <- system.file("extdata", "grada_R2.fastq", package = "GRADA")
seq <- system.file("extdata", "adapter_list.txt", package = "GRADA")
```

# Analyze the Sequences:
This will render the DataTable (DT) 

```{r grada_table()}
grada_analyze(PE = TRUE, seq = seq, read1 = read1, read2 = read2, M_min = 0)
```

## find the first position of the adapter sequence
This will find the 1. position of the sequence (for mismatch = 0) in every read (that contains the adapter)

- the data from grada_analyze() is needed!

```{r grada_analyze_positions()}
grada_analyze_positions(PE = TRUE, readlength = 125, numCores = 1)
```
# Table of results:
This will show the found adapters in a table.

- data from grada_analyze() is needed.

## DataTable (DT)

- for DT the package "DT" is needed.

```{r}
grada_table_DT()
```

## kable

```{r}
grada_table_simple()
```

# Plot the results:
This function will plot the found countings (for mismatch = 0)  

- data from grada_analyze() is needed.
- data from grada_analyze_positions() is needed!  

For the standard stettings all the three following commands are the same:

- `grada_plot_bar(PE = TRUE, input = "temp/", skip = TRUE, plot_row = 2, plot_col = 2)`
- `grada_plot_bar()`
- `grada_plot()`

```{r}
grada_plot_bar(PE = TRUE, skip = TRUE, plot_row = 1, plot_col = 1)
```
